Long name of the paper

### 2018-08-21 anzjs2018/anzjs2018.tex

>>>>

To generate arrival time predictions, 
several aspects of the vehicle's \emph{state} need to first be estimated,
such as its speed.
The \emph{unmeasurable state} of a vehicle at time $t_k$ is denoted by
\begin{equation}
    X_k = \begin{bmatrix} x_k & \dot x_k & \ddot x_k \end{bmatrix}^\top,
\end{equation}
where $x$ is the distance traveled along a route,
$\dot x$ is the speed (the first derivative of distance traveled as a function of time),
and $\ddot x$ is acceleration (the second derivative).

The next state is modeled as a function of the current state,
using a transition function $f$
